### 2016-06-21 ch05-initvals/initial-values.tex
Some recommendations private defense
Use glossaries for some parts of ch5

\section{Introduction}
\label{sec:initial-values:introd}
The task of interpreting measurement data from dynamic systems often involves the estimation of a \gls{TF}. 
Typical measurement techniques and identification strategies of  \glspl{TF} or \glspl{FRF} are presented in~\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
Application of these methods to real devices and systems is well-represented in the literature, e.g. \citep{Lim2010,Robinson1990,Behjat2010}.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/successRates.tikz}
 \caption[Simulated success rate of the different initialization schemes for varying SNR.]{The success rate $\successRate$  obtained using the smoothers, i.e. $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems. The $95\%$ confidence intervals~\eqref{eq:initvals:Binomial:CI} are indicated by bars.}
  \label{fig:successRateVS_SNR36N3dB}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.66\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/RMSEvs_SNR36N3dB-ripple6.tikz}
 \caption[Simulated model RMSE compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
 In the bottom plot, the difference between both is shown.
 Consequently, it makes sense to examine the behavior of the models in terms of $\model{\trueSymbol}$ as long as this RMSE meets the user's requirements.}
  \label{fig:RMSE}
\end{figure}

\paragraph*{Remark about the model quality}
In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\model{\trueSymbol}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\model{\trueSymbol}$ itself might be ill-suited.
A straightforward tool to analyze the error associated with $\hat{G}_0$ is to examine its relative RMS error over different realizations of the experiment.
In~\citep{Ljung1999}, a rule-of-thumb is given that describes the relationship between the SNR of the signals and the quality of the estimated parametric model.
In this context this heuristic boils down to: 
\begin{equation}
    \RMSE(\model{\trueSymbol}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm[2]{\true{G}}}{\SNR} 
    \label{eq:heur-RMSE}
\end{equation}
where $n_{\theta}=5$ is the number of estimated parameters in this case.
In \figref{fig:RMSE}, the empirical $\RMSE(\model{\trueSymbol})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the RMSE of the parametric estimate.
When the RMSE is then divided by $\norm[2]{\true{G}}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{\thisDir/figs/measurement.pdf}
  \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter. The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized. 
  Blue arrows indicate coax cables. 
  At the output of the bandpass filter, a noise generator is added that buffers the incoming signal using a TL071 opamp and adds white noise before passing the signal to the DAQ.} 
  \label{fig:measurementSetup}
\end{figure}

To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
The signal generation and acquisition was by means of a \gls{NI} Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
Although acquisition and generation were synchronized, there is a small delay $\tau_{\mathrm{MUX}} \approx 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$ due to the hardware architecture of the \gls{NI} Elvis II.
Particularly, the involved channels are captured by means of a single \gls{ADC} which is preceded by a multiplexer to select the active channel.
This obviously introduces a slight delay between the acquisition of a sample of input and output channels that is not part of system dynamics of the \BK{} filter, but rather of the experimental set-up.
As such, the output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau_{\mathrm{MUX}} \right)$ such that this inter-channel acquisition delay of the \gls{NI} Elvis is compensated; the time-domain counterpart $y(t)$ is obtained using the \gls{IDFT}.

>>>>

%TODO: more references, further back than Ljung
\section{Introduction}
\label{sec:initial-values:introd}
The task of interpreting measurement data from dynamic systems often involves the estimation of a \gls{TF}. 
Typical measurement techniques and identification strategies of  \glspl{TF} or \glspl{FRF} are presented in~\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
Application of these methods to real devices and systems is well-represented in the literature, e.g. \citep{Lim2010,Robinson1990,Behjat2010}.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/successRates.tikz}
 \caption[Simulated success rate of the different initialization schemes for varying \glsentryshort{SNR}.]{The success rate $\successRate$  obtained using the smoothers, i.e. $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems. The $95\%$ confidence intervals~\eqref{eq:initvals:Binomial:CI} are indicated by bars.}
  \label{fig:successRateVS_SNR36N3dB}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.66\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/RMSEvs_SNR36N3dB-ripple6.tikz}
 \caption[Simulated model \glsentryshort{RMSE} compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
 In the bottom plot, the difference between both is shown.
 Consequently, it makes sense to examine the behavior of the models in terms of $\model{\trueSymbol}$ as long as this RMSE meets the user's requirements.}
  \label{fig:RMSE}
\end{figure}

\paragraph*{Remark about the model quality}
In principle, convergence of the estimate $\model{\bullet}$ to the `best' estimate $\model{\trueSymbol}$ does not imply that $\model{\bullet}$ will be suitable for a specific purpose as the estimate $\model{\trueSymbol}$ itself might be ill-suited.
A straightforward tool to analyze the error associated with $\model{\trueSymbol}$ is to examine its relative \gls{RMS} error, with respect to the true system $\true{G}$, over different realizations of the experiment.
In~\citep{Ljung1999}, a rule-of-thumb is given that describes the relationship between the \gls{SNR} of the signals and the quality of the estimated parametric model.
In this context this heuristic boils down to: 
\begin{equation}
    \RMSE(\model{\trueSymbol}) \approx \sqrt{\frac{n_\theta}{N}} \frac{\norm[2]{\true{G}}}{\SNR} 
    \label{eq:heur-RMSE}
\end{equation}
where $n_{\theta}=5$ is the number of estimated parameters in this case.
In \figref{fig:RMSE}, the empirical $\RMSE(\model{\trueSymbol})$ over the different Monte Carlo runs is displayed against this rule-of-thumb.
It can be seen that these runs align almost perfectly, which shows that this rule-of-thumb can be used to approximate the \gls{RMSE} of the parametric estimate.
When the \gls{RMSE} is then divided by $\norm[2]{\true{G}}$, this graph essentially shows the anticipated relative error on the transfer function and, hence, gives an indication on its usability.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{\thisDir/figs/measurement.pdf}
  \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter. The \glsentryfirst{AWG} and \glsentryfirst{DAQ} hardware share the same clock and are thus synchronized. 
  Blue arrows indicate coax cables. 
  At the output of the bandpass filter, a noise generator is added that buffers the incoming signal using a TL071 opamp and adds white noise before passing the signal to the DAQ.} 
  \label{fig:measurementSetup}
\end{figure}

To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
The signal generation and acquisition was by means of a \gls{NI} Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
Although acquisition and generation were synchronized, there is a small delay $\tau_{\mathrm{MUX}} \approx 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$ due to the hardware architecture of the \gls{NI} Elvis~II.
Particularly, the involved channels are captured by means of a single \gls{ADC} which is preceded by a multiplexer to select the active channel.
This obviously introduces a slight delay between the acquisition of a sample of input and output channels that is not part of system dynamics of the \BK{} filter, but rather of the experimental set-up.
As such, the output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau_{\mathrm{MUX}} \right)$ such that this inter-channel acquisition delay of the \gls{NI} Elvis is compensated; the time-domain counterpart $y(t)$ is obtained using the \gls{IDFT}.
